TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-03-12 article.tex
TTT: detalles en la parte de descripci'on del m'etodo

\en{It is important to stress that the posterior, although similar, is not a Gaussian distribution, preventing us from using equation~\ref{eq:posterior_win} iteratively.}
\es{Es importante remarcar que la posterior, aunque se parezca, no es una distribuci\'on gaussiana, lo que nos impedir\'a usar la ecuaci\'on~\ref{eq:posterior_win} iterativamente.}
%
\en{But due to the shape of the exact posterior, a Gaussian distribution could be used as a good approximation, allowing us to avoid the computational cost of the sampling methodologies.}
\es{Por la forma del posterior exacto, una gaussiana puede ser usada como una buena aproximaci\'on, permiti\'endonos evitar el costo computacional de las metodolog\'ias de sampleo.}
%
\en{The main contribution of the Glicko system~\citep{glikman_gliko_2} was the development of an efficient method to approximate the exact posterior using a Gaussian distribution.}
\es{El principal aporte del sistema Glicko~\citep{glikman_gliko_2} fue el desarroll\'o de un m\'etodo eficiente para aproximar la posterior exacta con una distribuci\'on Gasussiana.}
%
\en{However, this method does not guarantee the quality of the approximation used.}
\es{Sin embargo, este m\'etodo no garantiza que la distribuci\'on gaussiana seleccionada sea la que mejor aproxima.}
%
\en{The success of the TrueSkill solution~\citep{Herbrich2007} is based on the application of an efficient method for computing the Gaussian distribution that guarantees the approximation of the posterior (section~\ref{sec:approximate_posterior}).}
\es{El \'exito de la soluci\'on TrueSkill~\citep{Herbrich2007} se basa en la aplicaci\'on de m\'etodo eficiente para calcular la gaussiana que mejor aproxima a la posterior exacta (secci\'on~\ref{sec:approximate_posterior}).}
%
\begin{equation} \label{eq:approx} 
 \widehat{p}(s_i| r, s_j) = \underset{\mu, \sigma}{\text{ arg min }} \ \ \text{KL}(\, p(s_i| r, s_j) \, || \,  \N(s_i|\mu, \sigma^2) \, )
\end{equation}
%
\en{which minimize the Kullback-Leibler divergence between the true and the approximate distribution. This kind of methods allows performing Bayesian inference in situations that otherwise would be impossible.}
\es{Esta clase de m\'etodos, que minizan la divergencia Kullback-Leibler entre la distribuci\'on verdadera y aproximada, permiten realizar inferencia bayesiana en situaciones que de otra forma no ser\'ia posibles.}
%
\en{In our case, in which we need to know how skills change over time, this technique allows us to efficiently apply equation~\ref{eq:posterior_win} iteratively over a sequence of observations.}
\es{En nuestro caso, en el que necesitamos conocer c\'omo cambian las habilidades a trav\'es del tiempo, est\'a t\'ecnica nos permite aplicar eficientemente la ecuaci\'on~\ref{eq:posterior_win} iterativamente sobre una secuencia de observaciones.}

\en{The approach adopted by TrueSkill to treat the dynamical process, known as \emph{filtering}, uses the posterior as the prior for the next event.}
\es{El enfoque adoptado por TrueSkill para tratar el proceso din\'amico, conocido como \emph{filtering}, usa el posterior como prior del siguiente evento.}
%
\en{Then, the posterior at any given time is,}
\es{Luego, el posterior en un determinado momento es,}
%
\begin{equation}\label{eq:filter} %\tag{\text{filtering}}
 \widehat{\text{Posterior}}_t \propto \widehat{\text{Likelihood}}_t  \overbrace{\widehat{\text{Likelihood}}_{t-1} \dots \widehat{\text{Likelihood}}_{2} \underbrace{\widehat{\text{Likelihood}}_{1} \text{Prior}_1}_{\widehat{\text{Posterior}}_{1} \text{ \en{as}\es{como} } \text{Prior}_{2}} }^{\widehat{\text{Posterior}}_{t-1} \text{ \en{as}\es{como} } \text{Prior}_{t}} %= \text{Prior}_1 \prod_{i=1}^t \text{Likelihood}_i 
\end{equation}
%
\en{where {\footnotesize $\widehat{\text{Posterior}}_i$} and {\footnotesize $\widehat{\text{Likelihood}}_i$} represents the approximations induced by the equation~\ref{eq:approx} at the $i$-th event.}
\es{Donde {\footnotesize $\widehat{\text{Posterior}}_i$} y {\footnotesize $\widehat{\text{Likelihood}}_i$} representan la aproximaciones inducidas por la ecuaci\'on~\ref{eq:approx} en el $i$-\'esimo evento.}
%
\en{If we consider the likelihood as a filter of the prior, each posterior can be seen as an accumulation of all previous filters.}
\es{Si consideramos la verosimilitud como un filtro del prior, cada posterior puede ser visto como una acumulaci\'on de todos los filtros anterios.}
%
\en{In this way, information propagates from past to future estimates.}
\es{De esta forma, la informaci\'on propaga del estimaciones pasadas hacia futuras.}
%
%\en{Learning is a dynamical process.}
%\es{El aprendizaje es un proceso din\'amico.}
%
\en{Since skills are dynamic variables it is important to incorporate a degree of uncertainty $\gamma$ at each step.}
\es{Debido a que las habilidades son variables din\'amicas es importante agregar alguna incertidumbre $\gamma$ en cada paso.}
%
\begin{equation}\label{eq:dynamic_factor}
 \widehat{p}(s_{i_t}) = \N(s_{i_t} | \mu_{i_{t-1}}, \sigma_{i_{t-1}}^2 + \gamma^2 )
 \end{equation}
 %
\en{Because the filtering approach does not arise from any probabilistic model, it suffers from some problems related to the fact that the information propagates in only one direction through the system.}
\es{Debido a que el enfoque de filtrado no se surge de ning\'un modelo probabil\'istico, sufre de un serie de problemas, todos relacionados con el hecho de que la informaci\'on se propaga en una sola direcci\'on a trav\'es del sistema.}
%
\en{The most obvious is that the beginning of any sequence of estimates always has high uncertainty.}
\es{El m\'as obvio es que el inicio de toda secuencia de estimaciones siempre tiene alta incertidumbre.}
%
\en{But it also suffers from ``temporary'' and ``spatial'' decoupling.}
\es{Pero tambi\'en sufre de desacoplamientos ``temporales'' y ``espaciales''.}
%
\en{Although the relative differences between current estimates within well-connected communities are correct, estimates separated in time and between poorly connected communities are often incorrect.}
\es{Aunque la diferencias relativas entre estimaciones contempor\'aneas al interior de comunidades bien conectadas sean correctas, las estimaciones separadas en el tiempo y entre comunidades poco conectadas suelen ser incorrectas.}
%

@@

\en{To obtain good initial estimates and ensure temporal and spatial comparability we need a causal model of the temporal process that links all historical activities.}
\es{A fin de obtener buenas estimaciones iniciales y garantizar comparbilidad temporal y espacial, necesitamos un modelo causal del proceso temporal que vincule todas las actividades hist\'oricas.}
\en{In any video game this typically involves evaluating a complex network made up of millions of events.}

@@

\en{This approach, known as \emph{smoothing}, is the one implemented by TrueSkill Through Time~\citep{Dangauthier2007}.}

@@

\en{By applying the rules of probability over this temporal model, historical information naturally propagate throughout the system, solving the problems of the filtering approach.}

@@

     \en{Graphical way of representing the factorization of the basic causal model (equation~\ref{eq:factorization}).}
     \es{Forma gráfica de representar la factorizaci\'on del modelo causal básico (ecuación~\ref{eq:factorization}).}

@@

\en{Since the observed results are independent of our beliefs, the only source of uncertainty comes from the variance of individual perfomances $\beta$.}

@@

\en{This is how we can define an equation that links the margin with the probability of a tie.}

>>>>

\en{It is important to stress that the posterior, although similar, is not a Gaussian distribution, preventing us from using equation~\ref{eq:posterior_win} iteratively.}
\es{Es importante remarcar que la posterior, aunque se parezca, no es una distribuci\'on gaussiana, lo que nos impedir\'a usar la ecuaci\'on~\ref{eq:posterior_win} iterativamente.}
%
\en{But due to the shape of the exact posterior, a Gaussian distribution could be used as a good approximation, allowing us to avoid the computational cost of the sampling methodologies.}
\es{Por la forma del posterior exacto, una gaussiana puede ser usada como una buena aproximaci\'on, permiti\'endonos evitar el costo computacional de las metodolog\'ias de sampleo.}
%
\en{The main contribution of the Glicko system~\citep{glikman_gliko_2} was the development of an efficient method to approximate the exact posterior using a Gaussian distribution.}
\es{El principal aporte del sistema Glicko~\citep{glikman_gliko_2} fue el desarroll\'o de un m\'etodo eficiente para aproximar la posterior exacta con una distribuci\'on Gasussiana.}
%
\en{However, this method does not guarantee the quality of the approximation used.}
\es{Sin embargo, este m\'etodo no garantiza que la distribuci\'on gaussiana seleccionada sea la que mejor aproxima.}
%
\en{The success of the TrueSkill solution~\citep{Herbrich2007} is based on the application of an efficient method for computing the Gaussian distribution that guarantees the approximation of the posterior (section~\ref{sec:approximate_posterior}).}
\es{El \'exito de la soluci\'on TrueSkill~\citep{Herbrich2007} se basa en la aplicaci\'on de m\'etodo eficiente para calcular la gaussiana que mejor aproxima a la posterior exacta (secci\'on~\ref{sec:approximate_posterior}).}
%
\begin{equation} \label{eq:approx} 
 \widehat{p}(s_i| r, s_j) = \underset{\mu, \sigma}{\text{ arg min }} \ \ \text{KL}(\, p(s_i| r, s_j) \, || \,  \N(s_i|\mu, \sigma^2) \, )
\end{equation}
%
\en{which minimizes the Kullback-Leibler divergence between the true and the approximate distribution. This kind of method allow performing Bayesian inference in situations that otherwise would be impossible.}
\es{Esta clase de m\'etodos, que minizan la divergencia Kullback-Leibler entre la distribuci\'on verdadera y aproximada, permiten realizar inferencia bayesiana en situaciones que de otra forma no ser\'ia posibles.}
%
\en{As we need to know how skills change over time, this technique allows to efficiently apply equation~\eqref{eq:posterior_win} iteratively over a sequence of observations.}
\es{En nuestro caso, en el que necesitamos conocer c\'omo cambian las habilidades a trav\'es del tiempo, est\'a t\'ecnica nos permite aplicar eficientemente la ecuaci\'on~\ref{eq:posterior_win} iterativamente sobre una secuencia de observaciones.}

\en{The approach adopted by TrueSkill to treat the dynamical process, known as \emph{filtering}, uses the posterior as the prior for the next event.}
\es{El enfoque adoptado por TrueSkill para tratar el proceso din\'amico, conocido como \emph{filtering}, usa el posterior como prior del siguiente evento.}
%
\en{The posterior at any given time is:}
\es{Luego, el posterior en un determinado momento es,}
%
\begin{equation}\label{eq:filter} %\tag{\text{filtering}}
 \widehat{\text{Posterior}}_t \propto \widehat{\text{Likelihood}}_t  \overbrace{\widehat{\text{Likelihood}}_{t-1} \dots \widehat{\text{Likelihood}}_{2} \underbrace{\widehat{\text{Likelihood}}_{1} \text{Prior}_1}_{\widehat{\text{Posterior}}_{1} \text{ \en{as}\es{como} } \text{Prior}_{2}} }^{\widehat{\text{Posterior}}_{t-1} \text{ \en{as}\es{como} } \text{Prior}_{t}} %= \text{Prior}_1 \prod_{i=1}^t \text{Likelihood}_i 
\end{equation}
%
\en{where {\footnotesize $\widehat{\text{Posterior}}_i$} and {\footnotesize $\widehat{\text{Likelihood}}_i$} represent the approximations induced by the equation~\eqref{eq:approx} at the $i$-th event.}
\es{Donde {\footnotesize $\widehat{\text{Posterior}}_i$} y {\footnotesize $\widehat{\text{Likelihood}}_i$} representan la aproximaciones inducidas por la ecuaci\'on~\eqref{eq:approx} en el $i$-\'esimo evento.}
%
\en{If we consider the likelihood as a filter of the prior, each posterior can be seen as an accumulation of all previous filters.}
\es{Si consideramos la verosimilitud como un filtro del prior, cada posterior puede ser visto como una acumulaci\'on de todos los filtros anterios.}
%
\en{In this way, information propagates from past to future estimates.}
\es{De esta forma, la informaci\'on propaga del estimaciones pasadas hacia futuras.}
%
%\en{Learning is a dynamical process.}
%\es{El aprendizaje es un proceso din\'amico.}
%
\en{Since skills are dynamic variables, it is important to incorporate a degree of uncertainty $\gamma$ at each step.}
\es{Debido a que las habilidades son variables din\'amicas, es importante agregar alguna incertidumbre $\gamma$ en cada paso.}
%
\begin{equation}\label{eq:dynamic_factor}
 \widehat{p}(s_{i_t}) = \N(s_{i_t} | \mu_{i_{t-1}}, \sigma_{i_{t-1}}^2 + \gamma^2 )
 \end{equation}
 %
\en{Because the filtering approach does not arise from any probabilistic model, it suffers from some limitations related to the fact that the information propagates in only one direction through the system.}
\es{Debido a que el enfoque de filtrado no se surge de ning\'un modelo probabil\'istico, sufre de un serie de problemas, todos relacionados con el hecho de que la informaci\'on se propaga en una sola direcci\'on a trav\'es del sistema.}
%
\en{The most obvious is that the beginning of any sequence of estimates always has high uncertainty.}
\es{El m\'as obvio es que el inicio de toda secuencia de estimaciones siempre tiene alta incertidumbre.}
%
\en{But it also suffers from ``temporary'' and ``spatial'' decoupling.}
\es{Pero tambi\'en sufre de desacoplamientos ``temporales'' y ``espaciales''.}
%
\en{Although the relative differences between current estimates within well-connected communities are correct, estimates separated in time and between poorly connected communities are often incorrect.}
\es{Aunque la diferencias relativas entre estimaciones contempor\'aneas al interior de comunidades bien conectadas sean correctas, las estimaciones separadas en el tiempo y entre comunidades poco conectadas suelen ser incorrectas.}
%

@@

\en{To obtain accurate initial estimates and ensure temporal and spatial comparability, we need a causal model of the dynamical process that links all historical activities.}
\es{A fin de obtener buenas estimaciones iniciales y garantizar comparabilidad temporal y espacial, necesitamos un modelo causal del proceso temporal que vincule todas las actividades hist\'oricas.}
\en{In any video game, this typically involves evaluating a complex network consisting of millions of events.}

@@

\en{This approach, known as \emph{smoothing}, is implemented by TrueSkill Through Time~\citep{Dangauthier2007}.}

@@

\en{By applying the rules of probability over this dynamical model, the historical information naturally propagates throughout the system, solving the issues caused by the filtering approach.}

@@

     \en{Graphical way of representing the factorization of the basic causal model (equation~\eqref{eq:factorization}).}
     \es{Forma gráfica de representar la factorizaci\'on del modelo causal básico (ecuación~\eqref{eq:factorization}).}

@@

\en{Since the observed results are independent of our beliefs, the only source of uncertainty comes from the variance of individual perfomance $\beta$.}

@@

\en{This is how we can define an expression that links the margin with the probability of a tie.}
